---
title: "workflow"
author: "Festus Nyasimi"
date: "3/26/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(refinery)
```


## Start a new blog post
```{r}
refinery::use_article_template(
  template = "_templates/standard_post.Rmd",
  slug = "creating-a-network",
  renv_new = FALSE)
```


## Initialise the _renv folder
```{r}
refinery::renv_new("2022-03-26_creating-a-network")
```

Write the blog

## Snapshot your env
```{r}
refinery::renv_snapshot("2022-03-26_creating-a-network")
```

## Restore
This is to get the same env for analysis
```{r}
refinery::renv_restore("2022-03-26_creating-a-network")
```

## Others
The `refinery::renv_restore()` function is a wrapper around renv::restore(). It updates the state of the local package library so that it mirrors the state of the lockfile

The `refinery::renv_delete()` function deletes all the renv infrastructure associated with a particular post. It exists so that you can wipe the local library, lockfile, etc, and start over.

Courtesy of [Navarro](https://blog.djnavarro.net/posts/2021-09-30_on-blogging-reproducibly/)
